\jaxcosmo: An End-to-End Differentiable and GPU Accelerated Cosmology Library

### 2023-01-13 paper_OJA.tex

\author{
J.~E. Campagne$^{1,\ast}$, 
F. Lanusse$^2$,
J. Zuntz$^3$,\\
D.~Kirkby$^4$,\\
Y.~Li$^{5,6}$,\\
A. Peel$^7$\\
\jaxcosmo\ contributors}
\thanks{$^\ast$jean-eric.campagne@ijclab.in2p3.fr}

@@

\affiliation{$^5$Department of Mathematics and Theory, Peng Cheng Laboratory, Shenzhen, Guangdong 518066, China}
\affiliation{$^6$Center for Computational Astrophysics \& Center for Computational Mathematics, Flatiron Institute, New York, New York 10010, USA}
\affiliation{$^7$Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, Switzerland}

@@

%%%
\section*{Credit authorship contribution statement}
\textbf{J.E Campagne:} Conceptualization, Methodology, Software, Validation, Writing, Visualization.
\textbf{F. Lanusse:}, Conceptualization, Methodology, Software, Validation, Writing, Project administration.
\textbf{J. Zuntz:} Investigation, Writing.
\textbf{D.~Kirkby:}, Software and validation for sparse linear algebra.
\textbf{A. Peel:} Software and validation for spline interpolations in JAX.

>>>>

\author{
J.~E. Campagne$^{1,\ast}$, 
F. Lanusse$^2$,
J. Zuntz$^3$,\\
A. Boucaud$^8$,
D.~Kirkby$^4$,
D. Lanzieri$^2$,
Y.~Li$^{5,6}$,
A. Peel$^7$
\jaxcosmo\ contributors}
\thanks{$^\ast$jean-eric.campagne@ijclab.in2p3.fr}

@@

\affiliation{$^5$Department of Mathematics and Theory, Peng Cheng Laboratory, Shenzhen, Guangdong 518066, China}
\affiliation{$^6$Center for Computational Astrophysics \& Center for Computational Mathematics, Flatiron Institute, New York, New York 10010, USA}
\affiliation{$^7$Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, Switzerland}
\affiliation{$^8$Université de Paris, CNRS, Astroparticule et Cosmologie, F-75013 Paris, France}

@@

%%%
\section*{Credit authorship contribution statement}
\textbf{A. Boucaud:} Software and comments.
\textbf{J.E Campagne:} Conceptualization, Methodology, Software, Validation, Writing, Visualization.
\textbf{F. Lanusse:} Conceptualization, Methodology, Software, Validation, Writing, Project administration.
\textbf{D. Lanzieri:} Software and validation for redshift distribution.
\textbf{J. Zuntz:} Investigation, Writing.
\textbf{D.~Kirkby:} Software and validation for sparse linear algebra.
\textbf{A. Peel:} Software and validation for spline interpolations in JAX.
